Informing forest carbon inventories under the Paris Agreement using the Global Forest Carbon Database (ForC v4.0)

### 2023-06-02 doc/manuscript/ESSDmanuscript.Rmd
Camille declined authorship

---
title: Informing forest carbon inventories under the Paris Agreement using the Global Forest Carbon Database (ForC v4.0)
journal: "`r rticles::copernicus_journal_abbreviations(journal_name = 'essd')`"
author:
  - given_name: Kristina J.
    surname: Anderson-Teixeira
    affiliation: "1,2 *"
    email: teixeirak@si.edu
    corresponding: true
  - given_name: Valentine
    surname: Herrmann
    affiliation: "1"
  - given_name: Madison 
    surname: Williams
    affiliation: "1"
  - given_name: Teagan
    surname: Rogers
    affiliation: "1"
  - given_name: Rebecca
    surname: Banbury Morgan
    affiliation: "1,3" 
  - given_name: Ben 
    surname: Bond-Lamberty
    affiliation: "4" 
  - given_name: Susan 
    surname: Cook-Patton
    affiliation: "5" 
  - given_name: Camille
    surname: Piponiot
    affiliation: "6"

affiliation:
  - code: 1
    address: Center for Conservation Ecology, Smithsonian's National Zoo & Conservation Biology Institute, Front Royal, VA, United States
  - code: 2
    address: Forest Global Earth Observatory, Smithsonian Tropical Research Institute, Panama, Republic of Panama
  - code: 3
    address: School of Geography, University of Leeds, Leeds, UK
  - code: 4
    address: Joint Global Change Research Institute, Pacific Northwest National Laboratory, College Park, MD, United States
  - code: 5
    address: The Nature Conservancy; Arlington VA 22203, USA
  - code: 6
    address: CIRAD, Montpellier, France
abstract: |

>>>>

---
title: Informing forest carbon inventories under the Paris Agreement using the Global Forest Carbon Database (ForC v4.0)
journal: "`r rticles::copernicus_journal_abbreviations(journal_name = 'essd')`"
author:
  - given_name: Kristina J.
    surname: Anderson-Teixeira
    affiliation: "1,2 *"
    email: teixeirak@si.edu
    corresponding: true
  - given_name: Valentine
    surname: Herrmann
    affiliation: "1"
  - given_name: Madison 
    surname: Williams
    affiliation: "1"
  - given_name: Teagan
    surname: Rogers
    affiliation: "1"
  - given_name: Rebecca
    surname: Banbury Morgan
    affiliation: "1,3" 
  - given_name: Ben 
    surname: Bond-Lamberty
    affiliation: "4" 
  - given_name: Susan 
    surname: Cook-Patton
    affiliation: "5"

affiliation:
  - code: 1
    address: Center for Conservation Ecology, Smithsonian's National Zoo & Conservation Biology Institute, Front Royal, VA, United States
  - code: 2
    address: Forest Global Earth Observatory, Smithsonian Tropical Research Institute, Panama, Republic of Panama
  - code: 3
    address: School of Geography, University of Leeds, Leeds, UK
  - code: 4
    address: Joint Global Change Research Institute, Pacific Northwest National Laboratory, College Park, MD, United States
  - code: 5
    address: The Nature Conservancy; Arlington VA 22203, USA

abstract: |
